---
title: "Bootstrapping"
output: github_document
---

```{r setup}
library(tidyverse)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Simulate data 

```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = 
  sim_df_const %>% 
  mutate(
    error = error * 0.75 * x, 
    y = 2 + 3 * x + error
  )
```

Plot the data set 

```{r}
sim_df_const %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm")
```

There is a linear observation - residual has a constabt variance alone the x axis. 
Assumptions for simple linear regression met . 


```{r}
sim_df_nonconst %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm")
```

The residual variance assumption is not met - CI would be wrong. Methods to build a CI won't work here. We can fit OLS but uncertainity cannot be determined with this dataset. 

To overcome this we conduct a bootstrap analysis - 

step 1 - Regress 

```{r}
lm(y ~ x, data = sim_df_const) %>%  broom::tidy()
lm(y ~ x, data = sim_df_nonconst) %>%  broom::tidy()
```

Step 2 - bootstrap 
## Draw one bootstrap sample 

```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE) %>% 
    arrange(x)
}
```

Sample size - dependent on CI so keep the same size of sample.

check if the function works - 

```{r}
boot_sample(sim_df_nonconst) %>% 
   ggplot(aes(x = x, y = y)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") + 
  ylim(-5, 16)
```

Get intercept and p value 

```{r}
boot_sample(sim_df_nonconst) %>% 
  lm(y ~x, data = .) %>% 
  broom::tidy()
```

